---
title: "Esoph Data Analysis"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# LOADING THE DATA AND VISUALIZING IT

```{r}
library(faraway)
library(stats)
```
```{r}
data(esoph)
summary(esoph)
str(esoph)
```
#CREATING A GENERALIZED LINEAR MODEL
```{r}
linear_model <- glm(cbind(ncases, ncontrols) ~ agegp + unclass(tobgp)
                                         + unclass(alcgp),
              data = esoph, family = binomial())
summary(linear_model)
```
#Checking for outliers in the model
```{r}
#Checking for outliers
residuals(linear_model,type = "response") 
```
#Calculating the confidence interval
```{r}
confint(linear_model)
```
The confidence intervals for all the attributes in the data are shown in the table above
The probability that a 25 year old who does not smoke or drink will get espophegal cancer is significantly low (close to zero).
#PREDICTING THE PROBABILITY OF A WOMAN HAVING CANCER
```{r}
agegp <- c("45-54")
agegp <- as.factor(agegp)
alcgp <- c("40-79")
alcgp <- as.factor(alcgp)
tobgp <- c(10-19)
tobgp <= as.numeric(tobgp)
woman_data <- data.frame(agegp, alcgp, tobgp)
prob <- predict(linear_model, woman_data)
prob
```

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
